Multi-Core Model Checking and Maximum Satisfiability Applied to Hardware-Software Partitioning

### 2016-08-26 Docs/IJES/journal.tex
review conclusions

There is no single tool for efficiently solving all HW-SW partitioning benchmarks. In particular, the best (proposed) solution is ESBMC-$\nu$Z, which solves $4$ out of $7$ benchmarks; ESBMC-$\nu$Z is faster than ILP in all supported benchmarks ({\it i.e.}, CRC$32$, Patricia, Dijkstra, Clustering), but it returns three TOs (timeouts) related to RC6, Fuzzy and Mars benchmarks.

@@

\textcolor{blue}{Regarding the amount of MOs, the sequential ESBMC approach has to explore all (possible) states until it finds the HW-SW partitioning solution; it starts from an extreme, where all variables are selected as software, and then incrementally tests one by one to check whether a given node will be implemented in software or in hardware. In contrast, all multi-core ESBMC approaches and ESBMC-$\nu$Z, are (heuristically) optimized to reach faster the HW/SW partitioning solution than the sequential one, without the need for exploring all states as the sequential ESBMC approach does. As a result, if the HW/SW partitioning problem grows in complexity, then the sequential ESBMC approach tends to easily reach MO due to the state-space explosion.}

@@

The clustering benchmark seems to be the limit to test the ESBMC (described) implementations; 
\textcolor{blue}{although more benchmarks with complexity similar to clustering should be included in future work for a more precise conclusion. Note, however, that more than $150$ nodes lead to TO and MO. ILP shows robustness and produces results even for a high number of nodes and edges, but limited to RC$6$ benchmark with $329$ nodes.}

>>>>

As observed in the experimental evaluation, there is no single tool for efficiently solving all HW-SW partitioning benchmarks. In particular, the best (proposed) solution is ESBMC-$\nu$Z, which solves $4$ out of $7$ benchmarks; ESBMC-$\nu$Z is faster than ILP in all supported benchmarks ({\it i.e.}, CRC$32$, Patricia, Dijkstra, Clustering), but it returns three TOs (timeouts) related to RC6, Fuzzy and Mars benchmarks.

@@

\textcolor{blue}{Regarding the amount of MOs, the sequential ESBMC approach has to explore all (possible) states until it finds the HW-SW partitioning solution; it starts from an extreme, where all variables are selected as software, and then incrementally tests one by one to check whether a given node will be implemented in software or in hardware. In contrast, all multi-core ESBMC approaches and ESBMC-$\nu$Z, are (heuristically) optimized to reach faster the HW/SW partitioning solution than the sequential one, without the need for exploring all states as the sequential ESBMC approach does. As a result, if the HW/SW partitioning problem grows in complexity, then the sequential ESBMC approach tends to easily reach MO due to the state-space explosion problem.}

@@

The clustering benchmark seems to be the limit to test the ESBMC (described) implementations; 
\textcolor{blue}{although more benchmarks with similar complexity to clustering should be included in future work for a more precise conclusion. Note, however, that more than $150$ nodes lead to TO and MO. ILP shows robustness and produces results even for a high number of nodes and edges, but limited to RC$6$ benchmark with $329$ nodes.}
